Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-27 journal/article.tex
Discussion

\begin{figure}[h]
  \begin{center}
    \includegraphics{graphics/reasonstochange_summary.pdf}
    \caption{Reasons why organizations started an agile transformation}
    \label{fig:reasonstochange_summary}
  \end{center}
\end{figure}

@@

>>>>

\begin{figure}[h]
  \begin{center}
    \includegraphics{graphics/reasonstochange_summary.pdf}
    \caption{Reasons why the studied organizations started an agile
             transformation}
    \label{fig:reasonstochange_summary}
  \end{center}
\end{figure}

@@

Grounded theory may not be able to provide a single generally applicable model
for transformation, at least not in a literature review made based on the
current agile transformation publications. This is because of two things.
First, the organizations seem to differ too much from each other. Secondly, the
published studies focus too much on isolated phenomena within the larger
transformation.
It would require too big of an interpretation to combine all the various cases
into one theoretical model. We have chosen to present transformatoins using an
elementary two-axial classification of transformations, and listings of
individual phenomena that typically occur in a transformation.
